Supplementary Material

### 2019-01-09 analyses/reproduce_analyses.Rmd
update fig. 3 with arrows and contours

# Format plots
AF_landscape_plots <- plot_grid(
  AF_plot_Diam.Clutch + theme(legend.position = "none", 
                              axis.title.x = element_blank(),
                             axis.text.x = element_blank()),
  AF_plot_Clutch.Pref + theme(legend.position = "none", 
                              axis.title.y = element_blank(),
                              axis.text.y = element_blank()) + xlab("Preference (SDs)"), 
  AF_plot_Diam.Pref + theme(legend.position = "none") + ylab("Preference (SDs)"), 
  nrow=2, align="hv", labels = "AUTO")

>>>>

# Arrow data
gradients_Diam.Clutch <- data.frame(Foodweb = c("Complex","Simple"),
                                    sc.Diam = c(0,0), 
                                    sc.log.Clutch = c(0,0), 
                                    xend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$mean,
                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean), 
                                    yend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch")$mean, 
                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch")$mean))

gradients_Clutch.Pref <- data.frame(Foodweb = c("Complex","Simple"),
                                    sc.sqrt.Pref = c(0,0), 
                                    sc.log.Clutch = c(0,0), 
                                    xend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref")$mean, 
                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref")$mean), 
                                    yend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch")$mean, 
                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch")$mean))

gradients_Diam.Pref <- data.frame(Foodweb = c("Complex","Simple"),
                                    sc.Diam = c(0,0), 
                                    sc.sqrt.Pref = c(0,0), 
                                    xend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$mean,
                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean), 
                                    yend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref")$mean, 
                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref")$mean))

# Set contour breaks
breaks <- predict(foodweb_model, newdata=data.frame(sc.Diam = c(0,0), sc.log.Clutch = c(0,0), sc.sqrt.Pref = c(0,0), Foodweb = c("Complex","Simple")), type="response", re.form=~0)

# Format plots
AF_landscape_plots <- plot_grid(
  AF_plot_Diam.Clutch + theme(legend.position = "none", 
                              axis.title.x = element_blank(),
                             axis.text.x = element_blank()) +
    stat_contour(aes(z = average), breaks = breaks, linetype = "dotted", color = "black") + # mean(RF_Diam.Pref$absolute_fitness$average)
    geom_segment(data = gradients_Diam.Clutch, 
                 aes(x = sc.Diam, y = sc.log.Clutch, xend = xend, yend = yend), 
                 arrow = arrow(length = unit(0.03, "npc"))),
  AF_plot_Clutch.Pref + theme(legend.position = "none", 
                              axis.title.y = element_blank(),
                              axis.text.y = element_blank()) + xlab("Preference (SDs)") +
    stat_contour(aes(z = average), breaks = breaks, linetype = "dotted", color = "black") +
    geom_segment(data = gradients_Clutch.Pref, 
                 aes(x = sc.sqrt.Pref, y = sc.log.Clutch, xend = xend, yend = yend), 
                 arrow = arrow(length = unit(0.03, "npc"))), 
  AF_plot_Diam.Pref + theme(legend.position = "none") + ylab("Preference (SDs)") +
    stat_contour(aes(z = average), breaks = breaks, linetype = "dotted", color = "black") +
    geom_segment(data = gradients_Diam.Pref, 
                 aes(x = sc.Diam, y = sc.sqrt.Pref, xend = xend, yend = yend), 
                 arrow = arrow(length = unit(0.03, "npc"))), 
  nrow=2, align="hv", labels = "AUTO")
